\documentclass[12pt]{article}

\usepackage{titlesec}
\usepackage{multicol}

% Format
\usepackage{times}
\usepackage[margin=1in]{geometry}
% \usepackage{indentfirst}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\columnsep}{1cm}
\linespread{1}
\pagestyle{empty}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\scshape\raggedright}{}{0em}{}[]

\begin{document}

% Title
{\Huge Christian Koertje}

\begin{multicols}{2}
    Masters Graduate Student \\
    Department of Systems Science \& Industial Engineering at Binghamton University \\
    504 Plaza Dr. Apt 7-G02

    \columnbreak
    https://ckoertje.github.io/ \\
    https://github.com/ckoertje \\
    ckoertj1@binghamton.edu \\
    (781)-635-9513
\end{multicols}

% Goals
\section{Goals/Research Interests}
To apply my training in physics and mathematics to complex problems in interdisciplinary studies. To understand the relationship between microscopic and macroscopic phenomena. Research interests include nonlinear dynamics and chaos, pattern formation, statistical mechanics, and information processing.

% Education
\section{Education}
\subsection{\textbf{M.S. Systems Science}, Binghamton University, SUNY \hfill (2023)}
\begin{itemize}
    \itemsep = 0em
    \item[] Specializations: Complex Systems Modeling and Simulation
    \item[] Thesis: ``Social Nucleation in Opinion Dynamics''
    \item[] Supervisors: Hiroki Sayama and Sang Won Yoon
\end{itemize}

\subsection{\textbf{B.S. Physics with Honors}, University of North Carolina Wilmington \hfill (2021)}
\begin{itemize}
    \itemsep = 0em
    \item[] Awards: Summa Cum Laude
    \item[] Thesis: ``Relativistic Dynamics: A Journey to the Center of a Black Hole"
    \item[] Supervisor: Russell Herman
\end{itemize}

\subsection{\textbf{B.A. Mathematics}, University of North Carolina Wilmington \hfill (2021)}
\begin{itemize}
    \itemsep = 0em
    \item[] Awards: Summa Cum Laude
    \item[] Senior Project: ``Nonlinear Dynamics of the Emden Fowler Equation''
\end{itemize}

%% publications
% \section{Publications}
% \subsection{Submitted}

%% Projects
\section{Research Experience}

\subsection{\textbf{Masters Research} \hfill (2021 -- 2023)}
\begin{itemize}
    \itemsep = 0em
    \item \textbf{Thesis} Conducted original research in opinion formation dynamics with the goal of understanding the effect of global access to information. Under the supervision of Hiroki Sayama, I studied a nonlinear-nonlocal partial differential equation both numerically and analytically. Additions of population dynamics lead to spatio-temporal chaos in the self-organizing patterns.
    \item \textbf{RTSync Corp.} Research project assistant for a company by contributing to the mathematical foundations of the DEVS theory of modeling and simulation. Projects were funded by government agencies including the MDA and AFRL. This work was under the supervision of Sang Won Yoon at Binghamton University and Bernard Zeigler of RTSync.
    \begin{enumerate}
        \itemsep = 0em
        \item \textbf{DVAST} Developed discrete event simulation in C++ for the ADEVS simulator for testing DEVS-based distributed computing.
        \item \textbf{SimPA} Contributed to the developement of parallel process capabilities using DEVS-based modeling in Java and MS4 Me (proprietary simulation software developed by RTSync).
    \end{enumerate}
\end{itemize}

\subsection{\textbf{Undergraduate Research} \hfill (2017 -- 2021)}
\begin{itemize}
    \itemsep = 0em
    \item \textbf{Thesis} Conducted exploratory research into the nonlinear dynamics of general relativity focusing on dynamics of black holes outside the event horizon and on the approach to the BKL singularity inside. This project involved familiarizing myself with techniques of differential geometry.
    \item \textbf{Complex Adaptive Systems Lab (CASL)} Aided in the study of pattern formation in coral reef ecosystems. Numerical studies were conducted by simulating a system of nonlinear partial differential equations in Python.
\end{itemize}

% Conferences
\section{Presentations}
\subsection{Conference Talks}
\begin{enumerate}
    \itemsep = 0em
    \item Koertje, C. \& Sayama, H. (2022). Stability of opinion formation PDE model based on expanded non-local perception kernel, Northeast Regional Conference on Complex Systems.
\end{enumerate}


%% Awards
\section{Awards}
\begin{enumerate}
    \itemsep = 0em
    \item \textbf{Adrian D. Hurst Mathematics Scholarship} \hfill (2020) \\
    Awarded to a rising junior, senior, or graduate student who has declared a major in mathematics or a student in a pre-engineering transfer program and is a full time student at UNCW.
    \item \textbf{Douglas Smith Scholarship of Mathematics} \hfill (2019) \\
    This scholarship is merit-based and awarded annually to an undergraduate student who has declared a major in the Department of Mathematics and Statistics.
\end{enumerate}

%% Teaching Experience
\section{Teaching Experience }
\textbf{Tutoring}, University of North Carolina Wilmington \hfill (2018 -- 2021)
\begin{itemize}
    \itemsep = 0em
    \item UNCW University Learning Center as part of the math services. Provided help for students in Math and Physics classes.
    \item Courses tutored include: Introductory Analysis, Calculus 1 \& 2, Multivariable Calculus, Differential Equations and Introductory Physics 1 \& 2 (both with and without calculus).
\end{itemize}

%% workshops
\section{Workshops Attended}
\textbf{ComSciCon-NY}, Cornell University \hfill (2022)
\begin{itemize}
    \itemsep = 0em
    \item Attended a 2 day virtual workshop on science communication. This included mini symposiums on the differences in communication with different audiences such as collegues, general public, and science enthusiasts.
\end{itemize}

\textbf{Physics in the Ground Beneath our Feet}, Princeton University \hfill (2022)
\begin{itemize}
    \itemsep = 0em
    \item Attended a 3 day workshop focused on applications of nonlinear and statistical physics to environmental and geoscience. Learned about the field of soft-matter physics and the plethora of interesting projects in fluid dynamics, geomorphology, and climate science.
\end{itemize}


% Academic Achievement
\section{Extracurriculars}
\begin{enumerate}
    \itemsep = 0em
    \item Member of Sigma Pi Sigma, the physics honors society \hfill (2019--)
    \item Member of Pi Mu Epsilon, the mathematics honors society \hfill (2021--)
    \item Vice President of the Society of Physics Students at UNCW \hfill (2020 -- 2021)
    \item Member of the Society of Physics Students at UNCW \hfill (2019 -- 2021)
    \item Member of the UNCW Math Club \hfill (2018 -- 2021)
    \item Member of the Society for Industrial and Applied Mathematics (SIAM) \hfill (2021--)
\end{enumerate}

%% references
\section{References}
\textbf{Hiroki Sayama, D.Sc.}, Binghamton University, SUNY
\begin{itemize}
    \itemsep = 0em
    \item[] Position: Professor of Systems Science
    \item[] Relationship: M.S. Supervisor
    \item[] Email: sayama@binghamton.edu
\end{itemize}

\textbf{Russell L. Herman, Ph.D.}, University of North Carolina Wilmington
\begin{itemize}
    \itemsep = 0em
    \item[] Position: Professor of Physics and Mathematics
    \item[] Relationship: Mentor and Honors Supervisor
    \item[] Email: hermanr@uncw.edu
    \item[] Phone: (910)-962-3722
\end{itemize}

\textbf{Dylan McNamara, Ph.D.}, University of North Carolina Wilmington
\begin{itemize}
    \itemsep = 0em
    \item[] Position: Professor of Physics and Physical Oceanography
    \item[] Relationship: Mentor
    \item[] Email: mcnamarad@uncw.edu
    \item[] Phone: (910)-962-2588
\end{itemize}

\end{document}
