\documentclass[12pt]{article}

\usepackage{titlesec}
\usepackage{multicol}

% Format
\usepackage{times}
\usepackage[margin=1in]{geometry}
% \usepackage{indentfirst}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\columnsep}{1cm}
\linespread{1}
\pagestyle{empty}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\scshape\raggedright}{}{0em}{}[]

\begin{document}

% Title
{\Huge Christian Koertje}

\begin{multicols}{2}
    Masters Graduate Student \\
    Department of Systems Science \& Industial Engineering at Binghamton University \\
    504 Plaza Dr. Apt 7-G02

    \columnbreak
    https://ckoertje.github.io/ \\
    https://github.com/ckoertje \\
    ckoertj1@binghamton.edu \\
    (781)-635-9513
\end{multicols}

% Goals
\section{Goals/Research Interests}
To apply my training in physics and mathematics to real world problems in physical sciences. Also, to continue life-long learning with a PhD and beyond. Research interests include nonlinear dynamics and chaos, complex systems, condensed matter physics, and applied mathematics.

% Education
\section{Education}
\subsection{\textbf{M.S. Systems Science}, Binghamton University, SUNY \hfill (2023)}
\begin{itemize}
    \itemsep = 0em
    \item[] Specializations: Complex Systems Modeling and Simulation
    \item[] Thesis: ``Social Nucleation in Opinion Dynamics''
    \item[] Supervisors: Hiroki Sayama and Sang Won Yoon
\end{itemize}

\subsection{\textbf{B.S. Physics with Honors}, University of North Carolina Wilmington \hfill (2021)}
\begin{itemize}
    \itemsep = 0em
    \item[] Awards: Summa Cum Laude
    \item[] Thesis: ``Relativistic Dynamics: A Journey to the Center of a Black Hole"
    \item[] Supervisor: Russell Herman
\end{itemize}

\subsection{\textbf{B.A. Mathematics}, University of North Carolina Wilmington \hfill (2021)}
\begin{itemize}
    \itemsep = 0em
    \item[] Awards: Summa Cum Laude
    \item[] Senior Project: ``Nonlinear Dynamics of the Emden Fowler Equation''
\end{itemize}

%% publications
\section{Publications}
\subsection{Submitted}

%% Projects
\section{Research Experience}

\subsection{Masters Thesis \hfill \textit{In Progress}}
\begin{itemize}
    \itemsep = 0em
    \item[] Social Nucleation in Opinion Dynamics
    \item[] Supervisor: Hiroki Sayama
\end{itemize}

\subsection{Research Project Assistant \hfill \textit{January 2022 -- Present}}
\begin{itemize}
    \itemsep = 0em
    \item[] DEVS-based Virtual AS-IS Simulation Test Platform (DVAST)
    \item[] Supervisors: Sang Won Yoon and Bernard Zeigler
\end{itemize}

\subsection{Research Project Assistant \hfill \textit{January 2022 -- Present}}
\begin{itemize}
    \itemsep = 0em
    \item[] Simulation Predictive Analytics (SimPA)
    \item[] Supervisors: Sang Won Yoon and Bernard Zeigler
\end{itemize}

\subsection{Research Project Assistant \hfill \textit{August 2021 -- December 2021}}
\begin{itemize}
    \itemsep = 0em
    \item[] Simulation project team member focused on central fill pharmacy automation.
    \item[] Supervisors: Sang Won Yoon and Soongeol Kwon
\end{itemize}

\subsection{Honors Thesis \hfill \textit{August 2020 -- May 2021}}
\begin{itemize}
    \itemsep = 0em
    \item[] ``Relativistic Dynamics: A Journey to the Center of a Black Hole"
    \item[] Supervisor: Russell Herman
    \item[] \textit{Black holes tend to be host myriad interesting problems in general relativity. Here we explored the different regions of spacetime in and around a black hole from a dynamical systems approach. BKL singularity dynamics present the signatures of chaos on the approach to a singularity.}
\end{itemize}

\subsection{Research Assistant \hfill \textit{January 2020 -- May 2020}}
\begin{itemize}
    \itemsep = 0em
    \item[] Emergent Pattern Formation of Algae in Coral Reef Systems (not published)
    \item[] Supervisor: Dylan McNamara
    \item[] \textit{Halimeda is a species of algae found in coral reefs to exhibit a hexagonal pattern formation which can be modeled by a reaction-diffusion system and numerically explored. We explored various techniques of nonlinear diffusion in numerical models.}
\end{itemize}

% Conferences
\section{Presentations}
\subsection{Conference Talks}
\begin{enumerate}
    \itemsep = 0em
    \item Koertje, C. \& Sayama, H. (2022). Stability of opinion formation PDE model based on expanded non-local perception kernel, Northeast Regional Conference on Complex Systems.
\end{enumerate}


%% Awards
\section{Awards}
\begin{enumerate}
    \itemsep = 0em
    \item \textbf{Adrian D. Hurst Mathematics Scholarship} \hfill (2020) \\
    Awarded to a rising junior, senior, or graduate student who has declared a major in mathematics or a student in a pre-engineering transfer program and is a full time student at UNCW.
    \item \textbf{Douglas Smith Scholarship of Mathematics} \hfill (2019) \\
    This scholarship is merit-based and awarded annually to an undergraduate student who has declared a major in the Department of Mathematics and Statistics.
\end{enumerate}

%% Teaching Experience
\section{Teaching Experience }
\textbf{Tutoring}, University of North Carolina Wilmington \hfill (2018 -- 2021)
\begin{itemize}
    \itemsep = 0em
    \item UNCW University Learning Center as part of the math services. Provided help for students in Math and Physics classes.
    \item Courses tutored include: Introductory Analysis, Calculus 1 \& 2, Multivariable Calculus, Differential Equations and Introductory Physics 1 \& 2 (both with and without calculus).
\end{itemize}

%% workshops
\section{Workshops Attended}
\textbf{ComSciCon-NY}, Cornell University \hfill (2022)
\begin{itemize}
    \itemsep = 0em
    \item
\end{itemize}

\textbf{Physics in the Ground Beneath our Feet}, Princeton University \hfill (2022)
\begin{itemize}
    \itemsep = 0em
    \item
\end{itemize}


% Academic Achievement
\section{Extracurriculars}
\begin{enumerate}
    \itemsep = 0em
    \item Member of Sigma Pi Sigma, the physics honors society \hfill (2019--)
    \item Member of Pi Mu Epsilon, the mathematics honors society \hfill (2021--)
    \item Vice President of the Society of Physics Students at UNCW \hfill (2020 -- 2021)
    \item Member of the Society of Physics Students at UNCW \hfill (2019 -- 2021)
    \item Member of the UNCW Math Club \hfill (2018 -- 2021)
    \item Member of the Society for Industrial and Applied Mathematics (SIAM) \hfill (2021--)
\end{enumerate}

%% references
\section{References}
\textbf{Hiroki Sayama, D.Sc.}, Binghamton University, SUNY
\begin{itemize}
    \itemsep = 0em
    \item[] Position: Professor of Systems Science
    \item[] Relationship: M.S. Supervisor
    \item[] Email: sayama@binghamton.edu
\end{itemize}

\textbf{Russell L. Herman, Ph.D.}, University of North Carolina Wilmington
\begin{itemize}
    \itemsep = 0em
    \item[] Position: Professor of Physics and Mathematics
    \item[] Relationship: Mentor and Honors Supervisor
    \item[] Email: hermanr@uncw.edu
    \item[] Phone: (910)-962-3722
\end{itemize}

\textbf{Dylan McNamara, Ph.D.}, University of North Carolina Wilmington
\begin{itemize}
    \itemsep = 0em
    \item[] Position: Professor of Physics and Physical Oceanography
    \item[] Relationship: Mentor
    \item[] Email: mcnamarad@uncw.edu
    \item[] Phone: (910)-962-2588
\end{itemize}

\end{document}
